

1. Select one of the weather time series from data_week.csv

2. Try the four combinations of beta (on/off) and gamma (on/off)

3. Present the plots of data series, trend, and seasonal components for each of the four combinations

4. Make out-of-sample forecast for 26 weeks with confidence bands. 

5. Recommend one forecasting model -- give your justification
```{r}
#install.packages(c("fpp2", "forecast", "TTR"), dependencies = TRUE, repos = "https://cloud.r-project.org")
```

```{r}
data <- read.csv("data_week.csv", sep=",",dec=".",header=T) 	# weekly data
rainfall <- data[,13]
```

#time series objects, trend and seasonal components
```{r}
xx <- ts(rainfall, frequency = 52, start = c(2015,1))
plot.ts(xx)

rainfall_d <- decompose(xx) 
trend <- rainfall_d$trend
seasonal <- rainfall_d$seasonal
random <- rainfall_d$random
plot.ts(cbind(xx,trend, seasonal, random))
```

# 1) beta true, gamma true
```{r}
out1 <- HoltWinters(xx, beta = TRUE, gamma = TRUE) 			
out1$fitted 									
plot(out1)
plot(out1$fitted)
```

# 2) beta true, gamma false
```{r}
out2 <- HoltWinters(xx, beta = TRUE, gamma = FALSE) 			
out2$fitted 									
plot(out2)	
plot(out2$fitted)
```

# 3) beta false, gamma true
```{r}
out3 <- HoltWinters(xx, beta = FALSE, gamma = TRUE) 			
out3$fitted 									
plot(out3)	
plot(out3$fitted)
```

# 4) beta false, gamma FALSE
```{r}
out4 <- HoltWinters(xx, beta = FALSE, gamma = FALSE) 			
out4$fitted 									
plot(out4)
plot(out4$fitted)
```

# Out of Sample Forcasts for beta true, gamma true
```{r}
out5 <- forecast:::forecast.HoltWinters(out1, h = 26, level = c(68, 95))	 
plot(out5)
```

# Out of Sample Forcasts for beta true, gamma false
```{r}
out6 <- forecast:::forecast.HoltWinters(out2, h = 26, level = c(68, 95))	 
plot(out6)
```

# Out of Sample Forcasts for beta false, gamma true
```{r}
out7 <- forecast:::forecast.HoltWinters(out3, h = 26, level = c(68, 95))	 
plot(out7)
```

# Out of Sample Forcasts for beta false, gamma false
```{r}
out8 <- forecast:::forecast.HoltWinters(out4, h = 26, level = c(68, 95))	 
plot(out8)
```